A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks

### 2013-09-20 PAPER/introduction.tex
Final strechting

Finally, \emph{defect rates}: while they are very hardly tolerated in mask
based top down design , the same nature of a bottom up self
assembled process cannot assume such a deterministic device placement
process.

These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be founded on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altought we can assume an architecture similar to the
one depicted in~\ref{fig:nana} as background, the topology discovery
problem is more general and not stricly dependent on any of the
underlying computing architectures.

@@

The main contribution presented in this paper is to bring the advantages of
a segment-based approach to deadlock freedom without requiring any topology graph,
external defect map or centralized algorithm execution.  We introduce DiSR, a first effort for a Distributed
Segment-based Routing in large scale DNA self assembled networks.
While maintaining similar properties to segment-based , the DiSR
approach is not intended to discover the "optimal" segment choice
(ideally reachable with the knowledge of the topology graph) but just
to demonstrate a concrete model that can fit into such complex,
irregular and large sized topologies.
Given the irregular/high-defect rates scenario discussed above, is essential
avoiding non-scalable or resource hungry solutions such as
centralized off-chip algorithms, tree-based approaches, virtual channels
or expensive implementations based on hardware redundancy.

@@

The DiSR approach presented in this work is a first attempt of
reaching the same goal of a segment based approach, that is
estabilishing segments, without requiring any topology graph or
centralized execution.

>>>>

Finally, \emph{defect rates}: while they are very hardly tolerated in mask
based top down design , the same nature of a bottom up self
assembled process cannot assume such a deterministic device placement
process, thus defect tolerance is something like a design requirement
more than a exception to be avoided.

These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be founded on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altought we can assume an architecture similar to the
one depicted in~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not stricly dependent on any of the
underlying computing architecture.

@@

In this paper we introduce DiSR, a first effort for a Distributed
Segment-based Routing in large scale DNA self assembled networks.
The main contribution is to bring the advantages of
a segment-based approach to deadlock freedom without requiring any topology graph,
external defect map or centralized algorithm execution. 
While maintaining similar properties to segment-based , the DiSR
approach is not intended to discover the "optimal" segment choice
(ideally reachable with the knowledge of the topology graph) but just
to demonstrate a concrete model that can fit into such complex,
irregular and large sized topologies.
Given the irregular/high-defect rates scenario discussed above, is essential
avoiding non-scalable or resource hungry solutions such as
centralized off-chip algorithms, tree-based approaches, virtual channels
or expensive implementations based on hardware redundancy.

@@

The DiSR approach presented in this work is a first attempt of
reaching the same goals of a segment based approach, that is
estabilishing segments, without requiring any topology graph or
centralized execution.
